---
title: "Butterflies"
author: "Amal Almutairy"
date: "10/21/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
```


## Butterflies:
```{r}

butterflies <- read_csv("Butterflies.csv") 

```

## Descriptive statistics

Wingspan: Standard Deviation, Mean and Summary

```{r pressure, echo=FALSE}
sd(Butterflies$wingspan, na.rm = TRUE) # is 1.565508
mean(Butterflies$wingspan, na.rm = TRUE) # is 5.365
summary(Butterflies$wingspan)
```

Speed

```{r}
sd(Butterflies$Speed, na.rm = TRUE) # is 4.186759
mean(Butterflies$Speed, na.rm = TRUE) # is 15.65
summary(Butterflies$Speed)
```


## Influencers of Speed

What are the greatest influencers of a butterfly's speed?

Does wingspan influenct speed?

```{r}
ggplot(butterflies, aes(x = wingspan, y = Speed))  +
  geom_point() +
  geom_smooth(se = FALSE, method ="lm")

```

Describe this quantitatively? i.e. 

- What is the model? 
- Is it significant? 
- Is the model appropriate for the data? 
- Can you define a different model?

The other continuous variable would be weight?

```{r}
ggplot(butterflies, aes(x = Weight, y = Speed))  +
  geom_point() +
  geom_smooth(se = FALSE, method ="lm")

```

Is there a combinatorial effect of weight and wingspan on the speed of a butterfly?

```{r}
ggplot(butterflies, aes(x = wingspan, y = Weight))  +
  geom_point() +
  geom_smooth(se = FALSE, method ="lm")

```
So weight and wingspan are "co-linear" so it's not surprising that weight doens't predict speed, since wingspan, we already doesn't. 


## Inferential Statistics
```{r}

# Inferential Statistics
Butterflies_lm <- lm(wingspan ~ Butterfly_N , data =  butterflies)

Butterflies_lm %>% 
  anova(Butterflies_lm)


```



